On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-05 tt_intro.tex
Technical commit

In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1. Our result, cases of arity 1 and 3 can only yield finite structures of size $O (n)$, and cases of arity 4 and more can only yield finite structures which is size of $O (n^2)$, and a case of arity 2 can yield infinite structures but they are only the zig-zag conformation shown in Fig.~\ref{TTT_zigzag}.

%In this section, we prove that unary oritatami system can form infinitely at delay 1 and arity 2 deterministically and moreover that the only infinite conformations which its oritatami system can yield is only the zig-zag conformation shown in Fig.\ref{TTT_zigzag}.

Let $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ be a deterministic oritatami system of delay 1. 
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.5\linewidth]{Fig/jordan_curve.png}
\caption{}
\label{fig:Jordan}
\end{figure}

>>>>

In this section, we consider Problem~\ref{prob:det_unary_length} at delay 1. 
Let $\Xi = (\Sigma, R, \delta, \alpha, \sigma, w)$ be a deterministic oritatami system of delay 1. 
For $i \geq 0$ let $C_i$ be the unique elongation of $\sigma$ by $w[1..i]$, that is, foldable by $\Xi$. Hence $C_0 = \sigma$.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.5\linewidth]{Fig/jordan_curve.png}
\caption{A tunnel divides the world into two. 
Getting through the tunnel leads us to another world. 
}
\label{fig:Jordan}
\end{figure}
